\textls[-0]{\thetitle}

### 2023-03-23 canonicitymodel.tex
Fix.

We state the fundamental property of logical relation here---in our proof relevant model, it is admitting that our model is really a model, and our syntax is the initial model so there is map from our syntax to our canonicity model:
\begin{lemma}[Fundamental Theorem of Logical Relation]
  If we have a (intrinsically well-typed) term $\goodTerm{\Gm}{t}{T}$, then we have its interpretation as a dependent function $\denotesC{t} : \prod_{\goodSub{\cdot}{\gm}{\Gm}} \prod_{\gm' \in \denotesC{\goodCtx{\Gm}{}}(\gm)}\denotesC{\goodType{\Gm}{T}{}}(\gm)(\gm')(\sub{t}{\gm})$
\end{lemma}

>>>>

We state the fundamental property of logical relation here---in our proof relevant model, it is admitting that our model is really a model, and our syntax is the initial model so there is map from our syntax to our canonicity model:
\begin{lemma}[Fundamental Theorem of Logical Relation]
  If we have a (intrinsically well-typed) term $\goodTerm{\Gm}{t}{T}$, then we have its interpretation as a dependent function \\ $\denotesC{t} : \prod_{\goodSub{\cdot}{\gm}{\Gm}} \prod_{\gm' \in \denotesC{\goodCtx{\Gm}{}}(\gm)}\denotesC{\goodType{\Gm}{T}{}}(\gm)(\gm')(\sub{t}{\gm})$
\end{lemma}
